\documentclass[a4paper,12pt]{article}
% packages!
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{booktabs}
\usepackage{color}
\usepackage{dirtree}
\usepackage{fancyhdr}
%\usepackage[cm]{fullpage}
\usepackage[width=14.5cm,
            height=25cm,
            top=2.5cm,
            inner=1.5cm,
            outer=1.5cm]{geometry}
\usepackage{graphicx}
\usepackage{grffile} % avoids errors when there are multiple dots in file names
\usepackage{listings}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{lmodern}
\usepackage{makecell}
\usepackage{natbib}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{pbox}
\usepackage{sansmath}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{xparse}
% Alter some LaTeX defaults for better treatment of figures:
    \renewcommand{\topfraction}{0.9}    % max fraction of floats at top
    \renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
    \setcounter{topnumber}{2}
    \setcounter{bottomnumber}{2}
    \setcounter{totalnumber}{4}     % 2 may work better
    \setcounter{dbltopnumber}{2}    % for 2-column pages
    \renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
    \renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
    \renewcommand{\floatpagefraction}{0.7}      % require fuller float pages
    \renewcommand{\dblfloatpagefraction}{0.7}   % require fuller float pages

\renewcommand*\familydefault{\sfdefault}
\sansmath

\definecolor{darkgreen}{rgb}{0,0.6,0}
\definecolor{darkred}{rgb}{0.85,0,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{graybg}{rgb}{0.95,0.95,0.95}

\newcommand{\cmark}{\textcolor{darkgreen}{\ding{51}}}%
\newcommand{\xmark}{\textcolor{darkred}{\ding{55}}}%
\newcommand{\smark}{\ding{72}}%
\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}

% set presets for Python code:
\lstdefinestyle{python}{
  language=Python
}
\lstdefinestyle{bash}{
  language=bash
}
\lstset{
   basicstyle={\footnotesize\ttfamily},
   showstringspaces=false,
   keywordstyle={\bfseries\color{blue}},
   numbers=none,
   numberstyle=\tiny\color{gray},
   commentstyle=\color{darkgreen},
   stringstyle=\color{mauve},
   breaklines=true,
   backgroundcolor=\color{graybg}
}

% Hurenkinder und Schusterjungen verhindern
\clubpenalty10000
\widowpenalty10000
\displaywidowpenalty=10000

%opening
\title{Documentation of the adapted Fractions Skill Score:\\
       Summed Area Table implementation (\texttt{fss\_SAT.py})}
\author{Phillip Scheffknecht}

\pagestyle{fancy}
\fancyhf{}
\rhead{\rightmark}
\lhead{FSS --- SAT method}
\rfoot{Page \thepage}

\begin{document}
\begin{spacing}{1.05}
\maketitle

\begin{abstract}
This document describes \texttt{fss\_SAT.py}, the summed area table (SAT)
implementation of the Fractions Skill Score (FSS). The implementation is based
on the reference code published by \citet{faggian2015}. We first recap the SAT
algorithm and its reference implementation, and then document the adaptations
and extensions made on top of it: a vectorised neighbourhood filter, a
BLAS-based score evaluation, additional threshold modes, percentile thresholds,
an over-estimation diagnostic, an ensemble (eFSS) variant, parallelisation over
thresholds, transparent handling of missing (NaN) data through per-window
valid-point weighting, and the continuous/weighted FSS (\texttt{CWFSS}). A final
section documents the automated cross-method test suite that guards these
adaptations.\\
\end{abstract}

\tableofcontents
\newpage

\include{fss_SAT_introduction}

\include{fss_SAT_baseline}

\include{fss_SAT_adaptations}

\include{fss_SAT_tests}

\begin{thebibliography}{9}
\bibitem[Faggian et al.(2015)]{faggian2015}
Faggian, N., Roux, B., Steinle, P. and Ebert, B., 2015:
\textit{Fast calculation of the fractions skill score.}
MAUSAM, \textbf{66}, 3, 457--466.

\bibitem[Roberts and Lean(2008)]{roberts2008}
Roberts, N. M. and Lean, H. W., 2008:
\textit{Scale-selective verification of rainfall accumulations from
high-resolution forecasts of convective events.}
Mon. Wea. Rev., \textbf{136}, 78--97.

\bibitem[Duc et al.(2013)]{duc2013}
Duc, L., Saito, K. and Seko, H., 2013:
\textit{Spatial-temporal fractions verification for high-resolution ensemble
forecasts.} Tellus A, \textbf{65}.
\end{thebibliography}

\end{spacing}
\end{document}
